\documentclass{resume} % Use the custom resume.cls style
\usepackage[dvipsnames]{xcolor}

\definecolor{DustyPurple}{RGB}{103,68,84}
% \definecolor{WinePurple}{RGB}{131,35,100}
\definecolor{WinePurple}{RGB}{240,108,100}
\definecolor{DustyGreen}{RGB}{91,107,6}
\usepackage[hidelinks = true]{hyperref}

\hypersetup{frenchlinks=true}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Heather Zinn Brooks}
\address{Homepage: \href{https://hzinnbrooks.github.io/}{\texttt{hzinnbrooks.github.io}}}
\address{
\href{https://scholar.google.com/citations?user=VoSBMPsAAAAJ\&hl=en\&oi=ao}{Google Scholar} \\ 
 \href{https://github.com/hzinnbrooks}{Github}
}
\address{Email: \texttt{hzinnbrooks@g.hmc.edu}} % Your phone number and email

\renewenvironment{rSection}[1]{
\sectionskip
\textcolor{WinePurple}{\MakeUppercase{#1}}
\sectionlineskip
\hrule
\begin{list}{}{
\setlength{\leftmargin}{1.5em}
}
\item[]
}{
\end{list}
}



\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{\bf Research Interests}
Dynamical systems, networks, complex systems, differential equations, math modeling 
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{\bf Academic Appointments}
{\bf Harvey Mudd College} \hfill \\ 
Assistant Professor of Mathematics\hfill {\em 2020 -- \dots} \\ 
Barbara Stokes Dewey Assistant Professor in the Life Sciences \hfill {\em 2022 -- \dots} 

{\bf University of California, Los Angeles} \hfill \\ 
CAM Visiting Assistant Professor of Mathematics \hfill {\em 2018 -- 2020}  \\
{\em Mentor: Mason Porter}
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{\bf Education}
{\bf Ph.D. Mathematics, University of Utah} \hfill {\em 2018} \\
{\em Dynamics and structure: from microtubule networks to population networks} \\
{\em Advisor: Paul Bressloﬀ} 

{\bf B.S. Applied Mathematics, University of Utah} \hfill {\em 2012} \\
Undergraduate Research Scholar \\
College of Science Research Award Finalist \\
{\em Advisor: Alla Borisyuk} 
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{\bf Publications} \itemsep -2pt

\medskip

\uppercase{{\bf Journal Articles}}

\begin{itemize}
    \item Topaz, C. M., {\bf Brooks, H. Z.}, Kan, U., Sandstede, B., \& Smith, C. M. (2025). \href{https://www.tandfonline.com/doi/full/10.1080/00029890.2024.2409608}{Diversity, identity, and data}.
    The American Mathematical Monthly 132 (1), 36-47.

    \item {\bf Brooks, H.Z.}, \& Porter, M.A. (2025). \href{(https://pubs.aip.org/aip/cha/article/35/1/013160/3333167)}{An ``opinion reproduction number'' for infodemics in a bounded-confidence content-spreading process on networks}.
    Chaos: An Interdisciplinary Journal of Nonlinear Science 35 (1).

    \item {\bf Brooks, H. Z.}, Chodrow, P. S., \& Porter, M. (2024). \href{https://epubs.siam.org/doi/pdf/10.1137/22M1527258}{Emergence of polarization in a sigmoidal bounded-confidence model of opinion dynamics}. 
    SIAM Journal on Applied Dynamical Systems 23 (2), 1442-1470.

    \item Hickok, A., Kureh, Y., {\bf Brooks, H. Z.}, Feng, M., \& Porter, M. A. (2022). \href{https://epubs.siam.org/doi/pdf/10.1137/21M1399427}{A bounded-confidence model of
    opinion dynamics on hypergraphs}. SIAM Journal on Applied Dynamical Systems, 21(1), 1–32.

    \item {\bf Brooks, H. Z.}, \& Porter, M. A. (2020). \href{https://link.aps.org/pdf/10.1103/PhysRevResearch.2.023041}{A model for the influence of media on the ideology of content in
    online social networks}. Physical Review Research, 2(2), 023041.

    \item Carroll, S. R., {\bf Brooks, H. Z.}, \& Bressloﬀ, P. C. (2020). \href{https://www.sciencedirect.com/science/article/am/pii/S0167278919300685}{Bifurcation analysis of pattern formation in a
    two-dimensional hybrid reaction–transport model}. Physica D: Nonlinear Phenomena, 402, 132274.

    \item Wilson, S. N., Sindi, S. S., {\bf Brooks, H. Z.}, Hohn, M. E., Price, C. R., Radunskaya, A. E., \dots Feﬀerman, N. H. (2020). \href{https://www.frontiersin.org/articles/10.3389/fevo.2020.00054/full}{How emergent social patterns in allogrooming combat parasitic infections}.
    Frontiers in Ecology and Evolution, 8, 54.

    \item {\bf Brooks, H. Z.}, \& Bressloﬀ, P. C. (2017). \href{https://link.aps.org/pdf/10.1103/PhysRevE.96.012413}{Turing mechanism for homeostatic control of synaptic density
    during C. elegans growth}. Physical Review E, 96(1), 012413.

    \item {\bf Brooks, H. Z.}, \& Bressloﬀ, P. C. (2016). \href{https://epubs.siam.org/doi/pdf/10.1137/16M1061205}{A mechanism for Turing pattern formation with active and
    passive transport}. SIAM Journal on Applied Dynamical Systems, 15(4), 1823–1843.

    \item {\bf Brooks, H. Z.}, \& Bressloﬀ, P. C. (2015). \href{https://link.aps.org/pdf/10.1103/PhysRevE.92.012704}{Quasicycles in the stochastic hybrid Morris–Lecar neural model}.
    Physical Review E, 92(1), 012704.

    \item Lawley, S. D., Tuft, M., \& {\bf Brooks, H. Z.} (2015). \href{https://link.aps.org/pdf/10.1103/PhysRevE.92.042709}{Coarse-graining intermittent intracellular transport:
    Two-and three-dimensional models}. Physical Review E, 92(4), 042709.
\end{itemize}

\uppercase{{\bf Books and Chapters}}

\begin{itemize}
    \item {\bf Brooks, H. Z.}, Feng, M., Porter, M. A., \& Volkening, A. (Editors). (2025). Mathematical and Computational Methods for Complex Social Systems (Vol. 80). American Mathematical Society.

    \item Zhao, L., Kim, R., Oremland, L. S., Chowkwale, M., de Pillis, L. G., \& {\bf Brooks, H. Z.} (2024). \href{https://library.oapen.org/bitstream/handle/20.500.12657/92672/1/978-3-031-58516-6.pdf#page=55}{A survey of
    mathematical modeling of hormonal contraception and the menstrual cycle}. 
    Mathematical Modeling for Women’s Health: Collaborative Workshop for Women in Mathematical Biology, 51-82. Cham: Springer Nature Switzerland.

    \item {\bf Brooks, H. Z.}, Hohn, M. E., Price, C. R., Radunskaya, A. E., Sindi, S. S., Williams, N. D., \dots Feﬀerman, N. H. (2018). \href{https://link.springer.com/chapter/10.1007/978-3-319-98083-6_3}{Mathematical analysis of the impact of social structure on ectoparasite load in
    allogrooming populations}. In Understanding complex biological systems with mathematics (pp. 47–61).
    Springer.

    \item Williams, N. D., {\bf Brooks, H. Z.}, Hohn, M. E., Price, C. R., Radunskaya, A. E., Sindi, S. S., \dots Feﬀerman, N. H. (2018). \href{https://link.springer.com/chapter/10.1007/978-3-319-98083-6_2}{How disease risks can impact the evolution of social behaviors and emergent
    population organization}. In Understanding complex biological systems with mathematics (pp. 31–46).
    Springer.
\end{itemize}

\uppercase{{\bf Expository Articles \& Outreach}}

\begin{itemize}
    \item {\bf Brooks, H. Z.} (2025). \href{https://arxiv.org/pdf/2302.00801}{A tutorial on networks of social systems: A mathematical modeling perspective.} Mathematical and Computational Methods for Complex Social Systems, 80, 115.

    \item Jones, Q., Meléndez, A. R. V., Mendible, A., Aminian, M., {\bf Brooks, H. Z.}, Alexander, N., \dots Chodrow, P.
    (2023). \href{https://arxiv.org/pdf/2303.09282}{Data science and social justice in the mathematics community}. Notices of the American Mathematical Society, 70(9), 1479-1489.

    \item {\bf Brooks, H. Z.}, Chen, Y., Feng, M., Kureh, Y. H., Porter, M. A., \& Volkening, A. (2020). How to move a
    SIAM minisymposium online from the comfort of your home. DSWeb: The Dynamical Systems Web.

    \item {\bf Brooks, H. Z.}, Kanjanasaratool, U., Kureh, Y. H., \& Porter, M. A. (2020). \href{https://www.frontiersin.org/articles/10.3389/frym.2020.577741/pdf}{Disease detectives: Using
    mathematics to forecast the spread of infectious diseases}. Frontiers for Young Minds, Vol. 8: 577741.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{rSection}
\newpage
\begin{rSection}{\bf Grants and Fellowships} \itemsep -2pt
    Innovation Accelerator Laboratory for Data Science and Social Impact \hfill {\em 2025} \\
    One of three projects selected for funding through the Harvey Mudd College Innovation Accelerator Initiative. \\
    Project Lead, \$240,000

    NSF MRI-2408259 \hfill {\em 2024} \\
    Track 1 Acquisition of a High-Performance Computing Cluster for Interdisciplinary Research at the Claremont Colleges \\
    Senior Personnel, \$918,485

    2022 Barbara Stokes Dewey Endowed Assistant Professorship in the Life Sciences \hfill {\em 2022} \\
    Designed to assist professors with their teaching and research interest at an early career stage.

    NSF DMS-2109239 \hfill {\em 2021--2024} \\
    Advances in bounded-confidence models on networks \\
    Principal Investigator, \$208,684

    OCAC Data Science Course Development Grant Award \hfill{\em 2021} \\ \$1,500

    MAA Project NExT Fellowship \hfill{\em 2019–2021} \\ \$5,000

    Stockham Medal for Conspicuously Eﬀective Teaching nominee \hfill {\em 2017} \\ \$1,000

    T. Benny and Gail T. Rushing Fellowship Award \hfill {\em 2017} \\ \$5,000

    Center for Teaching and Learning Excellence Graduate Fellowship \hfill {\em 2016} \\ \$15,000

    NSF Research Training Grant Fellowship RTG-1148230 \hfill {\em 2014--2016} \\ \$20,457 per year
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{\bf Student Research Mentorship}

    \item \textbf{Theo Rode (HMC '26)}, Inferring network structure of mathematical models of opinion dynamics. 

    \item \textbf{Camilo Morales (HMC '25)}, Measuring the similarity between trees of different order.

    \item \textbf{Tian Dong (HMC '24)}, Exploring sigmoidal bounded-confidence models with mean field methods. {\em Placement: PhD Mathematics, University of Michigan}

    \item \textbf{Kerria Pang-Naylor (HMC '25)}, Generating opinion distributions from data using binary classification models. {\em Goldwater Scholar}

    \item \textbf{Robert Bowden (HMC '25)}, Opinion dynamics on hypergraphs using sheaf-based techniques.
    {\em Placement: MS Mathematics, Cambridge University}

    \item \textbf{Emme McMullen (HMC '23)}, Network models of gender homophily in professional hierarchies.
    {\em Placement: PhD Applied Mathematics, University of Washington}

    \item \textbf{Julianna Schalkwyk (HMC '23) and Hector Tierno (HMC '23)}, Quantile Deffuant–Weisbuch model of opinion dynamics (co-mentor Jamie Haddock).
    {\em Placements: PhD CS, Georgia Tech; PhD Information and Computer Sciences, University of Massachusetts Amherst}

    \item \textbf{Ian de Marcellus (HMC '23)}, Numerical simulations for mean-field models of opinion dynamics.
    {\em Placement: Mathematics and Computer Science Tutor, Education Solutions}

    \item \textbf{Jasper Bown (HMC '24)}, Methods for inferring network parameters from cascade models of opinion dynamics.

    \item \textbf{Andy Liu (HMC '23)}, Heterogeneous topic interdependencies in opinion dynamics.
    {\em Placement: PhD Language and Information Technology, Carnegie Mellon}

    \item \textbf{Madelyn Andersen (HMC '22)}, {\em 2021 Giovanni Borrelli Fellowship Recipient}. Graphon varieties.  
    {\em Placement: PhD CS, MIT (NSF GRFP Award Recipient)}

    \item \textbf{Christina Catlett (Scripps '22)}, Multilayer bounded-confidence models with synchronous and asynchronous updating. 
    {\em Placement: PhD ESAM, Northwestern University}

    \item \textbf{Phousawanh Peaungvongpakdy (HMC '22)}, Media impact on opinion dynamics in adaptive social networks.
    {\em Placement: PhD Mathematics, Washington State University}

    \item \textbf{Solomon Valore-Caplan (HMC '22)}, The effects of homophily and community structure on consensus in bounded-confidence models.
    {\em Placement: PhD ESAM, Northwestern University}

    \item \textbf{Ruixiao Wang (UCLA '22)}, Dynamics of the glass ceiling on networks (co-mentor Mason Porter). 
    {\em Placement: PhD Statistics and Data Science, Yale University} 

    \item \textbf{Georgia Pope (HMC '21)}, Stability analysis of a mathematical model of hormonal contraception. 
    {\em Placement: MS Epidemiology, University of Washington}

    \item \textbf{Sneha Sambandam (UCLA '21) and Annie Zhang (UCLA '21)}, Spread of competing content on networks with bounded-confidence dynamics.
    {\em Placement: PhD CS, University of British Columbia (Sambandam) and MS Applied Math, University of Vermont (Zhang)}

    \item \textbf{Gabrielle Lorenzi (UCLA '21)}, Networks, bias, and self-segregation of women and minorities in academia (co-mentor Mason Porter). 
    {\em Placement: Data Scientist, T. Rowe Price}

    \item \textbf{Siqiao Mu (Caltech '21)}, {\em Summer Undergraduate Research Fellowship program at Caltech}. SEIR models on networks (co-mentors Mason Porter and Franca Hoffmann). 
    {\em Placement: PhD ESAM, Northwestern University}

    \item \textbf{Sujai Hiremath (Caltech '23)}, {\em Summer Undergraduate Research Fellowship program at Caltech}. Opinion formation on networks (co-mentors Mason Porter and Franca Hoffmann).
    
    \item \textbf{Zehan Chao (UCLA graduate student), Zheyuan Cui (UCLA '21), Avery Edson (UCLA '20), Cesar Guajardo (Santa Monica College '20), Yihuan Huang (UCLA '21), Xingjia Wang (UCLA '20), Zhanyuan Yin (UCLA '21)}, {\em California Research Training Program in Computational and Applied Math}. Evaluating effectiveness of the Gang Reduction and Youth Development Program with dynamic mode decomposition and machine learning techniques.
    
    \item \textbf{Alex Pan (Caltech '22)}, {\em Summer Undergraduate Research Fellowship program at Caltech}. Opinion formation on networks (co-mentors Mason Porter and Franca Hoffmann).
    
    \item \textbf{Marie Tuft (Utah '15)}, Quantitative analysis of virus trafficking in a biological cell (co-mentor Sean Lawley).
    
    \item \textbf{Oliver Richardson (Utah '17)}, Modeling learning on neural networks (co-mentor Sean Lawley).
    
    \item \textbf{Braden Schaer (Utah '15) and Anand Singh (Utah '16)}, Modeling diffusion of neurotransmitters (co-mentor Sean Lawley).

\end{rSection}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{\bf Teaching}

\medskip

{\bf HMC}

    \begin{itemize}
    \item \textbf{Math 118A: Introduction to Mathematical Biology}, Spring 2025
    \item \textbf{Math 198: Math Forum}, Spring 2025 (2 sections)
    \item \textbf{Math 198AI: Network Science}, Fall 2024
    \item \textbf{Math 181: Dynamical Systems}, Spring 2024
    \item \textbf{Math 180: Partial Differential Equations}, Fall 2022, Fall 2024
    \item \textbf{Math 189AB: Mathematics of Democracy}, Fall 2021
    \item \textbf{Math 73: Linear Algebra}, Spring 2021 (2 sections, online), Spring 2022 (2 sections), Spring 2023 (2 sections)
    \item \textbf{Math 131: Mathematical Analysis}, Fall 2020 (online), Fall 2022, Fall 2023 (2 sections), Spring 2024, Spring 2025
    \end{itemize}

{\bf UCLA}

    \begin{itemize}
    \item \textbf{Math 168: Introduction to Networks}, Spring 2020 (online)
    \item \textbf{Math 142: Mathematical Modeling}, Fall 2019
    \item \textbf{Math 197: Reading Course in Nonlinear Dynamics}, Spring 2019
    \item \textbf{Math 134: Linear and Nonlinear Systems of Differential Equations}, Fall 2018 and Winter 2019
    \end{itemize}

\uppercase{{\bf University of Utah}}

    \begin{itemize}
    \item \textbf{Math 3140: Vector Calculus and Partial Differential Equations}, Spring 2018
    \item \textbf{Math 1210: Calculus 1}, Fall 2017 (online)
    \item \textbf{Math 2270: Linear Algebra}, Spring 2017 
    \item \textbf{Math 3150: Partial Differential Equations for Engineers}, Summer 2016 and Fall 2016
    \item \textbf{Math 1050: College Algebra}, Summer 2013
    \item \textbf{Math 1010: Intermediate Algebra}, Spring 2013 and Spring 2014
    \item \textbf{Math 1030: Intro to Quantitative Reasoning}, Fall 2012
    \end{itemize}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{\bf Invited Talks}

\medskip

\uppercase{\textbf{Plenaries}}

\begin{itemize}
    \item[2022] Interdisciplinary Workshop on Contagion on Complex Social Systems, University of Colorado Boulder
    \item[] Dynamics Days, virtual
\end{itemize}

\uppercase{\textbf{Conference Talks}}
\begin{itemize}
    \item[2025] Minisymposium on Dynamical Systems on Networks and Fractals --- {\em SIAM Conference on Applied Dynamical Systems, Denver, CO}
    \item[] Patterns, Dynamics, and Data in Complex Systems --- {\em ICERM, Providence, RI} 
    \item[2024] Expository Talk on Maximium Likelihood Estimation and Opinion Dynamics --- {\em Practicum for Undergraduate Mathematicians in Inverse Problems and Data Assimilation, IPAM, Los Angeles, CA}
    \item[] Minisymposium on Quantitative Justice through Applied Data Science --- {\em SIAM Annual Meeting, Spokane, WA}
    \item[] Lightning Talk on Dynamics and Drivers of Gender Representation in Academic Mathematics --- {\em NetSci, Quebec, Canada}
    \item[] Special Session on Mathematical Modeling of Complex Ecological and Social Systems --- {\em AMS Western Sectional Meeting, San Francisco, CA}
    \item[2023] Session on Promoting Children's and Women's Health with Mathematical Modeling and Computational
    Approaches ---
    {\em AWM Research Symposium, Atlanta, GA}
    \item[] Minisymposium on Many-Agent Systems and Mean-Field Models for Socio-Economic and Life Sciences Dynamics ---
    {\em International Conference on Industrial and Applied Mathematics, Tokyo, Japan}
    \item[] Minisymposium on Dynamics of Decisions and Behavior in Social Systems ---
    {\em SIAM Conference on Applied Dynamical Systems, Portland, OR}
    \item[] Special Session on Little School Dynamics ---
    {\em Joint Mathematics Meeting, Boston, MA}
    \item[2022] Special Session on Mathematical Modeling of Biological and Social Systems ---
    {\em AMS Western Sectional Meeting, Salt Lake City, UT}
    \item[2021] Satellite on Higher-order Models in Network Science --- {\em NetSci, virtual}
    \item[] Minisymposium on Collective Behavior and Social Evolution --- {\em Society for Mathematical Biology, virtual}
    \item[] Minisymposium on Modeling Collective Behavior in Human Social Systems --- {\em SIAM Conference on Applied Dynamical Systems, virtual}
    \item[] Southern California Systems Biology Symposium, virtual
    \item[] Special Session on Agent-based Dynamics and Self-Organization in Biology ---
    {\em Joint Mathematics Meeting, virtual}
    \item[] Tutorial on Networks in Social Systems ---
    {\em AMS Short Course on Mathematical and Computational Methods for Complex Social Systems, virtual}
    \item[2019] Minisymposium on Mean-field Models for Large Interacting Agent Systems ---
    {\em SIAM Conference on Analysis of PDEs, La Quinta, CA}
    \item[] Session on Mathematical Biology: Multi-Scale Modeling of Complex Biological Systems ---
    {\em AMS Western Sectional Meeting, Riverside, CA}
    \item[] Minisymposium on Dynamics of Democracy ---
    {\em SIAM Conference on Applied Dynamical Systems, Snowbird, UT}
    \item[] Session on Advances in Mathematical Biology ---
    {\em Association for Women in Mathematics Research Symposium, Houston, TX}
    \item[] Session on Agent-Based Modeling in Biological and Social Systems ---
    {\em Joint Mathematics Meeting, Baltimore, MD}
    \item[2018] Minisymposium on Modeling Cell Motility and Cytoskeleton Interactions ---
    {\em SIAM Conference on Life Sciences, Minneapolis, MN}
    \item[] Session on Modeling Biological Rhythms ---
    {\em MAA MathFest, Denver, CO}
    \item[] Workshop Celebrating Diversity: Nonlinear Dynamics and Complex Systems ---
    {\em SIAM Annual Meeting, Portland, OR}
    \item[] Minisymposium on Spatial Dynamics: Local and Global Results ---
    {\em SIAM Conference on Nonlinear Waves and Coherent Strutures}
    \item[] Session on Modeling Disease and Biological Processes ---
    {\em Joint Mathematics Meeting, San Diego, CA}
    \item[2017] Society for Mathematical Biology, Salt Lake City, UT
    \item[2015] Stochastic Neural Dynamics Workshop ---
    {\em Organization for Computational Neuroscience, Prague, Czech Republic}
\end{itemize}

\uppercase{\textbf{Seminars and Colloquia}}
\begin{itemize}
    \item[2023] Applied Mathematics Colloquium, CU Boulder
    \item[] Mathematics Colloquium, Colorado School of Mines
    \item[] Mathematics Colloquium, UCLA
    \item[] Applied and Computational Mathematics Seminar, Dartmouth
    \item[] Mathematics Colloquium, Middlebury College
    \item[] Applied Math Seminar, UC Riverside
    \item[] Applied Math Seminar, UC Irvine
    \item[2022] Math Biology Seminar, Duke
    \item[2021] Little School Dynamics Colloquium, virtual
    \item[] Mathematical Sciences Colloquium, Appalachian State University, virtual
    \item[] Mathematics and Statistics Colloquium, College of the Holy Cross, virtual 
    \item[] ESAM Colloquium, Northwestern University, virtual
    \item[] Mathematics Colloquium, Claremont Colleges, virtual
    \item[2020] Dynamics Seminar, CU Boulder, virtual
    \item[] Women in Network Science Seminar, virtual
    \item[] Joint Applied Math Seminar, Claremont Colleges and University of Utah, virtual
    \item[] Networks Seminar, University of Houston, Houston, TX
    \item[2019] Probability Seminar, Tulane University, New Orleans, LA
    \item[] Computational Math + X Seminar, Caltech, Pasadena, CA
    \item[2018] Applied Math Seminar, Claremont Colleges, Claremont, CA
    \item[] Applied PDEs Seminar, Brigham Young University, Provo, UT
    \item[2017] Biophysics Seminar, UCLA, Los Angeles, CA
    \item[] Howard Hughes Medical Institute Summer Research Program, Claremont, CA
\end{itemize}

\newpage

\uppercase{\textbf{Workshops}}
\begin{itemize}
    \item[2022] Collaborative Workshop on Women in Mathematical Biology: Mathematical Approaches to Support Women's Health --- {\em Institute for Mathematics and its Applications, Minneapolis, MN}
    \item[2021] Workshop on Mathematics and Racial Justice --- {\em Mathematical Sciences Research Institute, virtual}
    \item[] Mathematical and Computational Approaches to Social Justice ---
    {\em ICERM workshop (virtual)}
    \item[] SMB Workshop on Equity, Diversity, and Inclusion ---
    {\em Society for Mathematical Biology, virtual}
    \item[2019] Applied Mathematical Modeling with Topological Techniques ---
    {\em ICERM workshop, Providence, RI}
    \item[] Learning in Networks ---
    {\em NIMBioS/DySoC Working Group, University of Tennessee, Knoxville, TN}
    \item[2018] Cultural Analytics ---
    {\em IPAM workshop, Lake Arrowhead Conference Center, CA}
    \item[] Agent-Based Modeling in Biological and Social Systems ---
    {\em AMS Mathematics Research Community, West Greenwich, RI}
    \item[2017] Women Advancing Mathematical Biology Workshop ---
    {\em MBI at The Ohio State University, Columbus, OH}
\end{itemize}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{\bf Service to the Profession}

\medskip

\uppercase{{\bf Organization of Conferences and Workshops}}
\begin{itemize}
    \item[2025]  {Collective Social Phenomena: Dynamics and Data} --- 
    {\em Workshop, Casa Matemática Oaxaca}
    %Co-organizers: Nancy Rodríguez, Maria D'Orsogna, Chad Topaz

    \item[] {SIAM Conference on Applied Dynamical Systems}  --- 
    {\em Organizing Committee Member}

    \item[2023]{Complex Social Systems}  ---
    {\em AMS Mathematics Research Community}
    %Co-organizers: Michelle Feng, Mason Porter, Alexandria Volkening

    \item[2022] {Building Networks: Women in Complex \& Nonlinear Systems} --- {\em Workshop, Banff International Research Station}
    %Co-organizers: Nina Fefferman, Nancy Rodríguez, Alexandria Volkening

    \item[] {Data Science and Social Justice: Networks, Policy, and Education} ---
    {\em Summer Research Program, ICERM} 
    
    \item[]
    {Interdisciplinary Network Analysis Methods for Analyzing Social Systems} --- {\em Workshop, ICERM}

    \item[] {Southern California Applied Math Symposium} ---
    {\em Conference, Harvey Mudd College}
    %Co-organizer: Jamie Haddock

    \item[2021] {Mathematical and Computational Methods for Complex Social Systems} ---
    {\em AMS Short Course, Joint Mathematics Meeting (virtual) }
    %Co-organizers: Michelle Feng, Mason Porter, Alexandria Volkening
\end{itemize}

\uppercase{{\bf Organization of Sessions and Minisymposia}}
\begin{itemize}
    \item[2024]  {Complex and Nonlinear Systems} ---
    {\em AWM Workshop, SIAM Annual Meeting}

    \item[2023] {Women in Network Science} ---
    {\em Minisymposium, SIAM Conference on Applied Dynamical Systems}

    \item[2022] {Mathematics of Complex Systems} ---
    {\em SIAM Special Session, Joint Mathematics Meeting }

    \item[] {Women in Math Biology} --- 
    {\em AMS Special Session, Joint Mathematics Meeting }

    \item[2021] {Novel Techniques for Modeling Biological Systems in the Age of Data} ---
    {\em Minisymposium, SIAM conference on Applied Dynamical Systems (virtual)}

    \item[2020] {Topological Data Analysis and Data-Driven Modeling in Complex Systems} ---
    {\em Minisymposium, SIAM conference on the Mathematics of Data Science (virtual)}

    \item[] {Women in Mathematical Biology} ---
    {\em AMS-AWM Special Session, Joint Mathematics Meeting }  
    %Co-organizers: Christina Edholm, Katharine Gurski, and Amanda Laubmeier

    \item[] {Interactive Session on Fostering Equitable Classrooms} ---
    {\em Project NExT Session, Joint Mathematics Meeting }

    \item[2019] {Disease Detectives: Stopping the Zombie Apocalypse with Mathematics} --
   {\em Booth at the UCLA Exploring Your Universe science festival on the role of mathematics and networks in epidemiology for Targeted toward families and children in the Los Angeles community.}

    \item[] {Dynamics of Democracy} ---
    {\em Minisymposium, SIAM Conference on Applied Dynamical Systems} 

    \item[] {Student and Postdoc Icebreaker Session} --- 
    {\em Introductory session for creating an inclusive environment for young researchers, SIAM conference on Applied Dynamical Systems}

\end{itemize}

\uppercase{{\bf Leadership Roles and Committees}} 

\begin{itemize}
    \item[2025] Conference Organizing Committee, SIAM Activity Group on Dynamical Systems 
    \item[2024] AWM SIAM Committee 
    \item[2023] Nominating Committee, SIAM Activity Group on Dynamical Systems
    \item[2022] President, Southern California SIAM Regional Section
\end{itemize}


\uppercase{{\bf Mentorship}}
\begin{itemize}
    \item[2025] Mentoring Session, 
    SIAM Conference on Applied Dynamical Systems 
    \item[] Red Sock Poster Judge, 
    SIAM Conference on Applied Dynamical Systems 
    \item[2024] Chair of AWM Minisymposterium, 
    SIAM Annual Meetings 
    \item[] Poster Judge, 
    Joint Mathematics Meetings
    \item[2023] Red Sock Poster Judge, 
    SIAM Conference on Applied Dynamical Systems
    \item[] Poster Judge, 
    Joint Mathematics Meetings
    \item[2022] Guided Activity Group on Network Science,
    SIAM Conference on Math of Data Science 
\end{itemize}

\uppercase{{\bf Peer Review}}

    AMS Notices \\
    Chaos \\
    La Matematica \\
    Nonlinearity \\
    Physica D \\
    Physical Review E \\
    PLoS ONE \\
    Royal Society Open Science \\
    SIAM Journal on Applied Mathematics \\
    SIAM Journal on Applied Dynamical Systems \\
    SIAM Review \\
    National Science Foundation Grants Review Panelist
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{\bf Institutional and Departmental Service}

\medskip

\uppercase{{\bf College Committee Service}}

Research Committee \hfill {\em 2025-\dots}
\\
Data Science Emphasis Program Committee (Co-Chair)  \hfill {\em 2023--\dots} 
\\
Assessment and Accreditation Committee \hfill {\em 2023--2024}
\\
Academic Aﬀairs Committee
\hfill {\em 2021--2023}

\uppercase{{\bf Department and Consortial Service}}

Faculty Advisor, Graduate School Guidance \hfill {\em 2023--\dots}
\\
Organizer, CCMS Applied Math Seminar \hfill {\em 2021--2023}
\\
Faculty Advisor, Gender Equity in Math Club \hfill {\em 2021--2023}
\\
Data Science Curricular Coherence Committee \hfill {\em 2020--2022}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
